---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}

library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrplot)
set.seed(041301)

```


#### Question 1
```{r}

setwd("~/Downloads/homework-2 4")

abalone_data <- read_csv(file = "data/abalone.csv")

age <- abalone_data[9] + 1.5

abalone_data_age <- cbind(age, abalone_data)

colnames(abalone_data_age)[1] <- "age"

hist(abalone_data_age$age)

```
Based off the histogram, we can see that abalone between the ages of 10 and 12 are most prevalent in this dataset. Abalone between the age of 12 and 14, as well as 8 and 10 are also observed frequently. Abalone older than 14 and younger than 8 are observed rarely.


#### Question 2
Code from Lab 2
```{r}

#Splitting abalone data into a training set and a testing set
abalone_split <- initial_split(abalone_data_age, prop = 0.80, strata = age)

abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)

```


#### Question 3
Code from Lab 2
```{r}

# Dummy coding categorical predictors, creating interactions
abalone_steps <- recipe(age ~ ., data = abalone_train) %>% step_dummy(all_nominal_predictors()) %>% step_scale(all_numeric_predictors()) %>% step_center(all_numeric_predictors()) %>% step_interact(terms = ~ type:shucked_weight + longest_shell:diameter + shucked_weight:shell_weight)

```



DID I USE STEP_INTERACT PROPERLY? EVERY TIME I ADD IT "lm_abalone_fit <- fit(lm_workflow, abalone_train)" STOPS WORKING

#### Question 4
Code from Lab 2
```{r}

lm_abalone_model <- linear_reg() %>% set_engine("lm")

```

```{r}
lm_workflow <- workflow() %>% add_model(lm_abalone_model) %>% add_recipe(abalone_steps)

lm_abalone_fit <- fit(lm_workflow, abalone_train)

#lm_abalone_fit %>% extract_fit_parsnip() %>% tidy()

```

Question 6:

```{r}

lm_abalone_model

lm_abalone_model <- linear_reg() %>% set_engine("lm") %>% fit(age ~ ., data = abalone_data_age)

#abalone_train_res <- predict(lm_abalone_fit, new_data = abalone_train %>% select(-age))

#head(abalone_train_res)

predict_input <- data.frame(longest_shell = 0.50, diameter = 0.10, height = 0.30, whole_weight = 4, shucked_weight = 1, viscera_weight = 2, shell_weight = 1)


#i <- c(1:7)

#predict_input[ , i] <- apply(predict_input[ , i], 7, function(x) as.numeric(as.character(x)))

#is.numeric(predict_input)

predict(lm_abalone_fit, new_data = predict_input %>% select(-age))

```



QUESTIONS:
DID I USE STEP_INTERACT PROPERLY? EVERY TIME I ADD IT "lm_abalone_fit <- fit(lm_workflow, abalone_train)" STOPS WORKING. NUMBER 3

QUESTION 6 PREDICT WONT WORK